---
title: "Clean Data"
author: "emchasen"
date: "2022-01-26"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

After moving the files that were downloaded in step one into my working directory, I created functions to read in the files with the same data from each of the counties, and bind them together. These data include properties of the horizon layers, soil components, mapunits, and representative component crop yields. 

### Function definitions

```{r}
#extract chorizon layers
library(tidyverse)

read_horizon <- function(){
  horizon <- list()
  for(i in 1:length(counties)){
    filename = paste0("data/", counties[i], "_SSURGO_chorizon.csv")
    horizon[[i]] <- read.csv(file = filename, na.strings = c(" ", "", "NA", "NaN"))
  }
  horizon <- do.call(rbind.data.frame, horizon)
}

#extract component layers
read_component <- function(){
  component <- list()
  for(i in 1:length(counties)){
    filename = paste0("data/", counties[i], "_SSURGO_component.csv")
    component[[i]] <- read.csv(file = filename, na.strings = c(" ", " ", "NA", "NaN"))
    component[[i]]$county <- counties[i]
  }
  component <- do.call(rbind.data.frame, component)
}

# #extract mapunit and attach county name
# read_mapunit <- function(){
#   mapunit <- list()
#   for(i in 1:length(counties)){
#     filename = paste0("data/", counties[i], "_SSURGO_mapunit.csv")
#     mapunit[[i]] <- read.csv(file = filename, na.strings = c(" ", "NA", "NaN", ""))
#   }
#   mapunit <- do.call(rbind.data.frame, mapunit)
# }

#extract component yields
read_cocropyld <- function(){
  cocropyld <- list()
  for(i in 1:length(counties)){
    filename = paste0("data/", counties[i], "_SSURGO_cocropyld.csv")
    cocropyld[[i]] <- read.csv(file = filename, na.strings = c("", NA, " ", "NaN"))
  }
  cocropyld <- do.call(rbind.data.frame, cocropyld)
}
```

## Read in data

```{r}
counties <- c("Brown", "Crawford", "Kewaunee", "Monroe", "Marathon", "Taylor", "Vernon", "Clark", "Grant","Shawano", "Lafayette", "Dane", "Chippewa", "Dodge", "FondDuLac", "Manitowoc", "Barron", "Adams", "Ashland", "Bayfield", "Buffalo","Burnett", "Columbia", "Door", "Douglas","Dunn", "EauClaire", "Florence", 'Forest', "Green", "GreenLake", "Iowa", "Iron","Jackson", "Jefferson", "Juneau", "LaCrosse", "Langlade","Lincoln", "Marinette","Marquette", "Menominee", "Oconto", "Oneida", "Outagamie", "Ozaukee", "Pepin", "Pierce","Polk", "Portage", "Price", "Richland", "Rock", "Rusk", "StCroix", "Sauk", "Sawyer","Sheboygan", "Trempealeau", "Vilas", "Walworth", "Washburn", "Washington", "Waupaca","Waushara", "Winnebago", "Wood", "CalumetManitowoc", "KenoshaRacine", "MilwaukeeWaukesha")

horizon <- read_horizon()
str(horizon)
component <- read_component()
str(component)
#mapunit <- read_mapunit()
#str(mapunit)
cocropyld <- read_cocropyld()
str(cocropyld)

```

## Clean horizon

Data was cleaned to include soil properties between 0-30 cm in depth, as well as a depth to bedrock and then filtered to include only pasture crops that were well represented across WI.

```{r}
#deepest horizon bottom of each component
depth <- horizon %>%
  group_by(cokey) %>%
  summarise(total.depth = max(hzdepb.r))

#filter to remove horizons that start below 30 cm
horizon <- horizon %>%
  filter(hzdept.r < 31) %>%
  droplevels()

colnames(horizon)

# select only variables of interest. Reference SSURGO_Metadata
horizon <- horizon %>%
  dplyr::select(hzdepb.r, hzdept.r, cokey, sandtotal.r, silttotal.r, claytotal.r, om.r, ksat.r, cec7.r, ph1to1h2o.r, awc.r)

summary(horizon)

#weighted means for the top 30 inches
horizon <- horizon %>%
  mutate(thick = ifelse(hzdepb.r > 30, 30 - hzdept.r, hzdepb.r - hzdept.r)) %>%  
  group_by(cokey) %>%
  summarise(sand = round(weighted.mean(sandtotal.r, thick, na.rm = TRUE),2),
            silt = round(weighted.mean(silttotal.r, thick, na.rm = TRUE),2),
            clay = round(weighted.mean(claytotal.r, thick, na.rm = TRUE),2),
            om = round(weighted.mean(om.r, thick, na.rm = TRUE),2),
            ksat = round(weighted.mean(ksat.r, thick, na.rm = TRUE),2),
            cec = round(weighted.mean(cec7.r, thick, na.rm = TRUE),2),
            ph = round(weighted.mean(ph1to1h2o.r, thick, na.rm = TRUE),2),
            awc = round(weighted.mean(awc.r, thick, na.rm = TRUE), 2)) 
#add deepest soil depth back
horizon <- left_join(horizon, depth, by = "cokey")
```

## Clean component

Select relevant variables and filter to component kind = Series. Filtering to series removes miscellaneous areas like water, landfills, coal mines. 

```{r}
names(component)
component <- component %>%
  dplyr::select(c(compname, compkind, slope = slope.r, elev = elev.r, mukey, cokey, county)) %>%
  filter(compkind == "Series") %>%
  droplevels()
str(component)
```

## Clean mapunit

```{r}
# names(mapunit)
# mapunit <- mapunit %>%
#   dplyr::select(c(mukey, county))
```

## Clean crop yields
```{r}
names(cocropyld)
cocropyld <- cocropyld %>%
  dplyr::select(cropname, yldunits, nonirryield.r, cokey)
levels(as.factor(cocropyld$cropname))
# filter to grasses/pasture with species names
grass_clover<- c("Bluegrass-white clover", "Orchardgrass-alsike", "Orchardgrass-red clover", "Timothy-alsike")
cocropyld <- cocropyld %>%
  filter(cropname %in% grass_clover) %>%
  drop_na()

summary(cocropyld)

# how many observations
cocropyld %>%
  group_by(cropname) %>%
  tally() %>%
  arrange(n)

```

## Join tables

```{r}
cropData <- left_join(component, horizon) %>%
  #left_join(mapunit) %>%
  left_join(cocropyld) %>%
  drop_na() %>%
  distinct() # remove duplicates
```

## Save data to file

```{r}
write.csv(cropData, "output/cropData.csv", row.names = FALSE, quote = FALSE)

```
