---
title: "Download Data"
author: "emchasen"
date: "2022-01-24"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Load libraries

The data needed for this analysis is stored in the SSURGO database. We used the R package FedData to download SSURGO data.

```{r}
library(FedData)
```

Download the data using the function get_ssurgo(). Give the argument 'template' the county area name, which are  'WI' + the county FIPS codes. However a few counties are joined together so it is helpful to reference the [Web Soil Survey](https://websoilsurvey.sc.egov.usda.gov/App/WebSoilSurvey.aspx). 
```{r, eval=FALSE}
Adams <- get_ssurgo(template = 'WI001', label = "Adams")
Ashland <- get_ssurgo(template = 'WI003', label = "Ashland")
Barron <- get_ssurgo(template= 'WI005', label='Barron')
Bayfield <- get_ssurgo(template = "WI007", label = "Bayfield")
Brown <- get_ssurgo(template= 'WI009', label='Brown')
Buffalo <- get_ssurgo(template = 'WI011', label = "Buffalo")
BurnettCounty <- get_ssurgo(template = 'WI013', label = "Burnett")
# 015 is Calumet county and that is combined with Manitowoc in WI600
Chippewa <- get_ssurgo(template= 'WI017', label='Chippewa')
Clark <- get_ssurgo(template= 'WI019', label='Clark')
Columbia <- get_ssurgo(template = 'WI021', label = "Columbia")
Crawford <- get_ssurgo(template= 'WI023', label='Crawford')
Dane <- get_ssurgo(template= 'WI025', label='Dane')
Dodge <- get_ssurgo(template= 'WI027', label='Dodge')
Door <- get_ssurgo(template = 'WI029', label = "Door")
Douglas<- get_ssurgo(template = 'WI031', label = "Douglas")
Dunn <- get_ssurgo(template =  'WI033', label = "Dunn")
EauClaire <- get_ssurgo(template = 'WI035', label = "EauClaire")
Florence <- get_ssurgo(template = 'WI037', label = "Florence")
FondDuLac <- get_ssurgo(template= 'WI039', label='FondDuLac')
Forest <- get_ssurgo(template = 'WI041', label = 'Forest')
Grant <- get_ssurgo(template= 'WI043', label='Grant')
Green <- get_ssurgo(template = 'WI045', label = "Green")
GreenLake <- get_ssurgo(template = 'WI047', label = "GreenLake")
Iowa <- get_ssurgo(template = 'WI049', label = "Iowa")
Iron <- get_ssurgo(template = 'WI051', label = "Iron")
Jackson <- get_ssurgo(template = 'WI053', label = "Jackson")
Jefferson <- get_ssurgo(template = 'WI055', label = "Jefferson")
Juneau <- get_ssurgo(template = 'WI057', label = "Juneau")
# 059 is Kenosha and that is joined with Racine in WI601
Kewaunee <- get_ssurgo(template= 'WI061', label='Kewaunee')
Lacrosse <- get_ssurgo(template = 'WI063', label = "LaCrosse")
Lafayette <- get_ssurgo(template= 'WI065', label='Lafayette')
Langlade <- get_ssurgo(template = 'WI067', label = "Langlade")
Lincoln <- get_ssurgo(template = 'WI069', label = "Lincoln")
# 071 is Manitowoc and that is joined with Calumet in WI600
Marathon <- get_ssurgo(template= 'WI073', label='Marathon')
Marinette <- get_ssurgo(template = 'WI075', label = "Marinette")
Marquette <- get_ssurgo(template = "WI077", label = "Marquette")
Menominee<- get_ssurgo(template = 'WI078', label = "Menominee")
# 079 is Milwaukee and that is joined with Waukesha in WI602
Monroe <- get_ssurgo(template= 'WI081', label='Monroe')
Oconto <- get_ssurgo(template = 'WI083', label = "Oconto")
Oneida<- get_ssurgo(template = 'WI085', label = "Oneida")
Outagamie <- get_ssurgo(template = "WI087", label = "Outagamie")
Ozaukee <- get_ssurgo(template = "WI089", label = "Ozaukee")
Pepin <- get_ssurgo(template = "WI091", label = "Pepin")
Pierce <- get_ssurgo(template = "WI093", label = "Pierce")
Polk <- get_ssurgo(template = "WI095", label = "Polk")
Portage <- get_ssurgo(template = "WI097", label = "Portage")
Price <- get_ssurgo(template = "WI099", label = "Price")
# 101 is Racine and that is combined with Kenosha in WI601
Richland <- get_ssurgo(template = "WI103", label = "Richland")
Rock <- get_ssurgo(template = "WI105", label = "Rock")
Rusk <- get_ssurgo(template = "WI107", label = "Rusk")
StCroix <- get_ssurgo(template = "WI109", label = "StCroix")
Sauk <- get_ssurgo(template = "WI111", label = "Sauk")
Sawyer <- get_ssurgo(template = "WI113", label = "Sawyer")
Shawano <- get_ssurgo(template= 'WI115', label='Shawano')
Sheboygan <- get_ssurgo(template = "WI117", label = "Sheboygan")
Taylor <- get_ssurgo(template= 'WI119', label='Taylor')
Trempealeau <- get_ssurgo(template = "WI121", label = "Trempealeau")
Vernon <- get_ssurgo(template= 'WI123', label='Vernon')
Vilas <- get_ssurgo(template = "WI125", label = "Vilas")
Walworth <- get_ssurgo(template = "WI127", label = "Walworth")
Washburn <- get_ssurgo(template = "WI129", label = "Washburn")
Washington <- get_ssurgo(template = "WI131", label = "Washington")
Waupaca <- get_ssurgo(template = "WI135", label = "Waupaca")
Waushara <- get_ssurgo(template = "WI137", label = "Waushara")
Winnebago <- get_ssurgo(template = "WI139", label = "Winnebago")
Wood <- get_ssurgo(template = "WI141", label = "Wood")
CalumetManitowoc <- get_ssurgo(template = "WI600", label = "CalumetManitowoc")
KenoshaRacine <- get_ssurgo(template = "WI601", label = "KenoshaRacine")
MilwaukeeWaukesha <- get_ssurgo(template = "WI602", label = "MilwaukeeWaukesha")
```

The data is now downloaded and accessible in your working directory.
